\textcolor{black}{5G will provide the fundamental infrastructure for building smart cities, which will push mobile network performance and capability requirements to their extremes.
\item Low latency and extremely high reliability, however, will also be essential requirements for the likes of mobile industrial automation, vehicular connectivity, and other IoT applications. Applications like smart sensors and text-based messaging are examples of extremely high-volume applications that will require very low data rates and will not be sensitive to latency.}

% \begin{enumerate}
% \item	Reliability, which, for example, could depend on whether they are estimates or more direct evidence;
% \item	Representativity, which is about how typical the data are; for example, you may have arguments why the very few cases are typical or you may carry out statistical tests;
% \item Validity, which is about the relevance of the data for your case. Strictly speaking, sometimes no valid data are available but one may argue that there are other data which could be used as ‘proxies’.) 
% \end{enumerate}
}
\section{How 5G will enhance the finance industry}
From ATM machines to online and mobile banking, the financial services industry has often been an early adopter of digital technology.
\item According to research done by ATT and IDG, 81 percent of financial institutions have made technology changes at the corporate and/or branch level in recent years.
\item With mobile usage continuing to accelerate at a rapid pace, many customers are actively seeking new services to match the evolving technologies in their pockets and on their wrists. To meet these demands, banks must be more agile than ever.
5G technology is poised to help banks and other finance companies deliver the new, innovative mobile services consumers want.


% \section{Finance and BAT}
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ut ipsum nec orci interdum sollicitudin ut eu nunc. Pellentesque ultricies eros in justo sagittis, eget blandit velit aliquet. Aenean ac lectus nibh. Quisque ac est pellentesque, ullamcorper sem sit amet, pharetra quam. Morbi ullamcorper placerat diam, sed tincidunt odio.

\section{Beyond customers}
5G’s benefits are expected to extend beyond customers. Financial professionals will also be able to use them to create more efficient back-end processes.
\item In insurance, damage appraisers could use 5G-enabled high-speed connectivity to send dozens of photos back to the head office quickly, without having to wait to reach their office or home network. Using this technology, insurance companies could serve customers more quickly and automatically, especially when combining claims adjustment processes with AI.
The future of financial services is mobile. As 5G enhancements create more reliable, responsive networks, they can help banks and other financial institutions ensure that this future is more productive, efficient and protected.


\subsection{Political Stage}
\subsubsection{America VS China}
When it comes to these two potential countries, it makes us wonder what exactly is 5G technology? And what is the deal with 5G? We might be tempted to think it is simply 4G but a little bit faster. In reality, it is a lot faster, so fast in fact that it can change the world as we have mentioned above briefly.
\item The new world of 5G technology promises to transform our lives by connecting millions of devices and enabling everything from driverless cars to smart homes. Up to 20 times faster than the 4G most of us use now, 5G’s lightning-fast technology will accelerate and interconnect everything
\item Downloading a two-hour film on 3G would take about 26 hours, on 4G you would be waiting six minutes, and on 5G you would be ready to watch the film in just over three and half seconds, what a world.
\item 5G is not only about download speeds, it is a game changer for everything. With 5G it is possible to have cities where everything is able to communicate. For example, doctors could perform surgeries from the other side of the world. Can you imagine a world where your videos never buffer, and your calls never drop?
\item There is no denying the technology is great. But. . . why do China and the U.S. care so much about who develops it?
\item The same reason they care about anything: there is a funny term “Benjamins” (i.e., money).
\item When the U.S. won the 4G race earlier this decade, it provided a nearly 100 billion boost to the gross domestic product. The stakes of the 5G race are even higher. If the U.S. wins, it will create an estimated three million jobs and add approximately 500 billion to GDP.
\item However, the fight over 5G is not just about money, and downloading films. No, it is also or mostly about power. If you control 5G access to everything people are doing online, you control everything.
\item Right now, the best 5G technology is made by the company Huawei. As this company is Chinese, many governments do not trust that the 5G will be secure.
\item Critics fear that allowing China to build 5G could enable the Chinese to spy on other countries or even to switch off the flow of data we will all depend on.
\item Imagine if Huawei becomes the leading 5G provider in the world, then China could spy on everyone, which is terrible for the U.S., because that is what the U.S. intends to do.
Those are the stakes: jobs, money and power.
\item While America is developing its own 5G, China’s 5G is so far ahead it will set the trends.
This is a race many people are saying the U.S. have already lost. Luckily, the U.S. have a maniac on their team who is willing to play dirty.
\item May 16: President Trump signed an executive order banning U.S. companies from using Telecom equipment deemed to be a national security threat. And that is a direct shot at China and tech giant Huawei.
\item Donald Trump could see the U.S. was not going to win, so he got a crowbar and pulled a Tonya Harding on China’s 5G.
\item Finally, President Trump cannot really be blamed for his actions, because how else can the U.S. win this race? Even if the U.S. do manage to cripple Huawei and China, it is not like the U.S. will suddenly have great 5G. You will not just have 5G overnight. Unless the U.S. pretends that it does.
\item It is a race that might be lost for the U.S., because this is considered the new space race. So maybe the U.S. can win this race the same way it won the last one (just fake it).

% \subsection{America VS China}

% \section{Huawei and ZTE}